	\vspace{0.5cm}	

We are highly indebted to the Department of Electronics and Computer Engineering, Central Campus Pulchowk, for providing us with this opportunity of collaborative undertaking which has helped us develop a major project of our own that has greatly enhanced our knowledge and provided us a new experience of team-work, which is quite important for our future endeavours.

We would like to express our deep sense of gratitude to our project supervisor, Dr. Dibakar Raj Pant, Head of Department, Department of Electronics and Computer Engineering, Pulchowk Campus, for providing us with lot of inspiration and intellectual guidance while also being very encouraging and supportive throughout the project period.

We would like to acknowledge Prof. Dr. Dinesh Kumar Sharma, Department of Electronics and Computer Engineering, Pulchowk Campus who guided and supported our project.

We would like to express our sincere gratitude to Er. Sanjeev Singh Kathayat, Deputy Director of Civil Aviation Authority of Nepal, whose immense encouragement and guidance have been quintessential in the overall success of our project. 

We would also like to thank Er. Ruraj Joshi, who guided us in debugging hardware and software problems related to the project. 

We would like to thank the Village Tech Solutions for believing in us and providing us the opportunity to work on this project.

We would also like to thank Real Time Solutions Pvt. Ltd., and 360 Consultancy  Pvt. Ltd., who provided us with workspaces and technical guidances during the project period. 

We would like to express our sincere gratitude to the Robotics Club, Central Campus Pulchowk and its members for providing us the various machineries and tools required to complete the hardware of the project.

We would also like to thank our friends and families, who supported us immensely throughout the project period. 

Lastly, we would like to thank everyone who helped us directly or indirectly during the project.